
\documentclass[11pt,letterpaper]{article}

% Load some basic packages that are useful to have
% and that should be part of any LaTeX installation.
%
% be able to include figures
\usepackage{graphicx}
% get nice colors
\usepackage{xcolor}

% change default font to Palatino (looks nicer!)
\usepackage[latin1]{inputenc}
\usepackage{mathpazo}
\usepackage[T1]{fontenc}
% load some useful math symbols/fonts
\usepackage{latexsym,amsfonts,amsmath,amssymb}

% comfort package to easily set margins
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

% control some spacings
%
% spacing after a paragraph
\setlength{\parskip}{.15cm}
% indentation at the top of a new paragraph
\setlength{\parindent}{0.0cm}


\begin{document}

\begin{center}
\Large
Ay190 -- Worksheet 9\\
Anthony Alvarez\\
Date: February 11, 2014
\end{center}

\section{Linear System of Equations}
\subsection{The data}

I have written functions which load in a matrix and determines if it is a square
invertable matrix. Even if it does not satisfy these conditoins the funciton
returns the matrix, as well as printing its size. I also have written a function
which loads in vectors, returns them as well as printing their size. 

\subsection{My Gauss Elimination}
I found a Gauss Elimination script on the internet. I have modified it to take
advantage of the numpy array functionality. This has provided a 55x speed up 
over the original implementation for the 1000x1000 matrix. 

In order to gauge the time it took more accurately (accounting for other 
processes changing over time) I ran multiple runs; 5 trials for all except the 
smallest matrix which went so quickly that 500 runs were required to get an 
accurate measure. I found that the my Gauss elimination method took 
$(0.00164, 0.138, 0.56, 18.148, 88.07)$ for each of the matricies $(10, 100, 200,
1000,2000)$ respectively. 

\subsection{Numpy Solver}

The Numpy linalg uses the LAPACK routine\_gesv to compute the solution. When
running the Numpy solver I found it was much quicker and thus required more
trials to accurately measure its speed. I ran 1000 trials for the matricies of
dimension 10, 100, and 200; 100 trials for the 1000 and 2000 row matrix. I 
found that it took $(9*10^{-5}, 1.22*10^{-3}, 5.82*10^{-3}, .5007, 3.63)$
seconds to complete for the $(10, 100, 200, 1000,2000)$ matricies respectively. 

\end{document}




